Type Refinements for the Working Class

### 2015-11-14 paper.tex
[paper] Use \varprojlim instead of Ran
@freebroccolo I'm just doing this for now since it's at least clear that
this works, and I don't quite know how to use Ran well enough to make it
work here (since it seems we accidentally introduced a requirement for
terminal objects in W). Please feel free to adjust this as you like
though.
lattice on refinements

\newcommand\TyBase[1]{\mathtt{Base}_{#1}}
\newcommand\TyTop[1]{\top_{#1}}

@@

  For any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\square\Omega}}$, we can define
  the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows, where
  $\Of{\Yoneda{-}}{\mathcal{W}\ra\mathbb{J}}$ is the Yoneda Embedding:
  \begin{align*}
    \ADefine{
      \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
    }{
      \Hom{\mathbb{J}}{
        \Yoneda{w}
      }{
        Ran_{\mathbbold{1}}{\mathcal{J}}
      }
    }\\
    &\cong
    \OMode{
      \int_{(w',\,\vec{E})}{{w'}\succeq{w}\Rightarrow{\mathcal{J}(\vec{E})(w')}}
    }
  \end{align*}

@@

\subsubsection{Equality of parametric refinement}

Two refinements are equal when they denote the same PER.\@That is, will define
the refinement equality judgment $\EqRefines{\Phi}{\phi}{\psi}{\tau}$ as
follows, presupposing $\RefinesCtx{\Phi}{\Upsilon}$,
$\Refines{\Phi}{\phi}{\tau}$ and $\Refines{\Phi}{\psi}{\tau}$:
\begin{definition}
  To know $\EqRefines{\Phi}{\phi}{\psi}{\tau}$ is to know, for any substitution
  $\Of{\rho}{\Upsilon\inj\OMode{\Upsilon'}}$, the following judgments:
  \begin{gather*}
    \GenJ{
      \MV{m},\MV{n}:\tau
    }{
      \HypJ{
        \IMode{M}\sim^\rho_\phi\IMode{N}
      }{
        \IMode{M}\sim^\rho_\psi\IMode{N}
      }
    }\\
    \GenJ{
      \MV{m},\MV{n}:\tau
    }{
      \HypJ{
        \IMode{M}\sim^\rho_\psi\IMode{N}
      }{
        \IMode{M}\sim^\rho_\phi\IMode{N}
      }
    }
  \end{gather*}

 %% and for any $M, N$
 %% such that $\IsAbt{\cdot}{\Upsilon'}{\cdot}{M}{\tau}$ and
 %% $\IsAbt{\cdot}{\Upsilon'}{\cdot}{N}{\tau}$,
 %% $\IMode{M}\sim^\rho_\phi\IMode{N}$ if and only if
 %% $\IMode{M}\sim^\rho_\psi\IMode{N}$.
\end{definition}

@@

>>>>

\newcommand\SubRefines[4]{\IMode{#1}\parallel\IMode{#2}\subseteq\IMode{#3}\sqsubset\OMode{#4}}
\newcommand\TyBase[1]{\mathtt{Base}_{#1}}
\newcommand\TyTop[1]{\top_{#1}}
\newcommand\TyBot[1]{\bot_{#1}}
\newcommand\TyMeet[1]{\cap_{#1}}
\newcommand\TyJoin[1]{\cup_{#1}}

@@

  For any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\square\Omega}}$, we can define
  the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows, where
  $\Of{\Yoneda{-}}{\mathcal{W}\ra\mathbb{J}}$ is the Yoneda Embedding:
  \begin{align*}
    \ADefine{
      \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
    }{
      \Hom{\mathbb{J}}{
        \Yoneda{w}
      }{
        \varprojlim\mathcal{J}
      }
    }\\
    &\cong
    \OMode{
      \int_{(w',\,\vec{E})}{{w'}\succeq{w}\Rightarrow{\mathcal{J}(\vec{E})(w')}}
    }
  \end{align*}

@@

\subsubsection{Ordering and Equality of Parametric Refinement}

We will write $\SubRefines{\Phi}{\phi}{\psi}{\tau}$ to mean that $\phi$ is a
\emph{subrefinement} of $\psi$, presupposing $\RefinesCtx{\Phi}{\Upsilon}$,
$\Refines{\Upsilon}{\phi}{\tau}$ and $\Refines{\Upsilon}{\psi}{\tau}$:
\begin{definition}
  To know $\SubRefines{\Phi}{\phi}{\psi}{\tau}$ is to know, for any substitution
  $\Of{\rho}{\Upsilon\inj\OMode{\Upsilon'}}$, the following judgments:
  \[
    \GenJ{
      \MV{m},\MV{n}:\tau
    }{
      \HypJ{
        \IMode{M}\sim^\rho_\psi\IMode{N}
      }{
        \IMode{M}\sim^\rho_\phi\IMode{N}
      }
    }
  \]
\end{definition}

Two refinements are equal when they denote the same PER. That is, we have
$\EqRefines{\Phi}{\phi}{\psi}{\tau}$ just when both
$\SubRefines{\Phi}{\phi}{\psi}{\tau}$ and $\SubRefines{\Phi}{\psi}{\phi}{\tau}$.

@@

\section{Constructions on Refinements}

Refinements can be arranged in a partial order via the
$\SubRefines{\Phi}{\phi}{\psi}{\tau}$ judgment, and admit a lattice structure
at any sort $\tau$.

We have the bottom refinement $\GRefines{\TyBot{\tau}}{\tau}$, which simply
contains no elements. Next, the top refinement $\GRefines{\TyTop{\tau}}{\tau}$
identifies all terms $M,N$ such that $\IsAbt{\cdot}{\Upsilon}{\cdot}{M}{\tau}$
and $\IsAbt{\cdot}{\Upsilon}{\cdot}{N}{\tau}$. The join
$\Refines{\Phi}{\phi\TyJoin{\tau}\psi}{\tau}$ of two refinements
$\Refines{\Phi}{\phi}{\tau}$ and $\Refines{\Phi}{\psi}{\tau}$ is defined as follows:
\begin{gather*}
  \infer{
    \RMemEq{\Phi}{M}{N}{\phi\TyJoin{\tau}\psi}
  }{
    \RMemEq{\Phi}{M}{N}{\phi}
  }\qquad
  \infer{
    \RMemEq{\Phi}{M}{N}{\phi\TyJoin{\tau}\psi}
  }{
    \RMemEq{\Phi}{M}{N}{\psi}
  }
\end{gather*}

Finally the meet $\Refines{\Phi}{\phi\TyMeet{\tau}\psi}{\tau}$ of two refinements
$\Refines{\Phi}{\phi}{\tau}$ and $\Refines{\Phi}{\psi}{\tau}$ is defined
dually:
\[
  \infer{
    \RMemEq{\Phi}{M}{N}{\phi\TyMeet{\tau}\psi}
  }{
    \RMemEq{\Phi}{M}{N}{\phi} &
    \RMemEq{\Phi}{M}{N}{\psi}
  }
\]

It is trivial to verify that these constructions on refinements give rise to a
lattice.
